MJSAI: Designing a Sound, Configurable, Efficient, and Pushdown Monadic Static~Analyzer for JavaScript

### 2014-12-13 cs252r-fa14-writeup/paper.tex
Add a lstlisting for data Frame

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% LstListings

\usepackage{listings}
\lstset{
  frame=none,
  xleftmargin=2pt,
  stepnumber=1,
  numbers=left,
  numbersep=5pt,
  numberstyle=\ttfamily\tiny\color[gray]{0.3},
  belowcaptionskip=\bigskipamount,
  captionpos=b,
  escapeinside={*'}{'*},
  language=haskell,
  tabsize=2,
  emphstyle={\bf},
  commentstyle=\it,
  stringstyle=\mdseries\rmfamily,
  showspaces=false,
  keywordstyle=\bfseries\rmfamily,
  columns=flexible,
  basicstyle=\small\sffamily,
  showstringspaces=false,
  morecomment=[l]\%,
}

@@

\begin{lstlisting}
data Frame =
    LetK [(Name, Set AValue)] Name [(Name, TExp)] TExp
  | AppL [TExp]
  | AppR (Set AValue) [(Set AValue)] [TExp]
  | ObjK [(String, (Set AValue))] Name [(Name, TExp)]
    -- Array Dereferencing
  | FieldRefL TExp
  | FieldRefR (Set AValue)
    -- Array Assignment
  | FieldSetA TExp         TExp
  | FieldSetN (Set AValue) TExp
  | FieldSetV (Set AValue) (Set AValue)
    -- Property Deletion
  | DeleteL TExp
  | DeleteR (Set AValue)
    -- Fig 2. Mutable References
  | RefSetL TExp
  | RefSetR (Set AValue)
  | RefK
  | DeRefK
    -- Fig 8. Control Operators
  | IfK TExp TExp
  | SeqK TExp
  | WhileL TExp TExp
  | WhileR TExp TExp
  | LabelK Label
  | BreakK Label
  | TryCatchK TExp Name
  | TryFinallyL TExp
  | TryFinallyR (Set AValue)
  | ThrowK
    -- Fig 9. Primitive Operations
  | PrimOpK Op [(Set AValue)] [TExp]
  deriving (Eq, Ord)
instance PartialOrder Frame where pcompare = discreteOrder
\end{lstlisting}

\end{figure}
